|

### 2021-09-28 paper.Rmd
name chunks

```{r, echo = FALSE}
# linear regression models with 0-1 rescaled DV
lm_knowledge_safe <- lm(rescale(knowledge_safe) ~ exp_group, data)
lm_policy_opinion <- lm(rescale(policy_opinion) ~ exp_group, data)
lm_moral_conviction <- lm(rescale(moral_conviction) ~ exp_group, data)

>>>>

```{r main-analysis, echo = FALSE}
# linear regression models with 0-1 rescaled DV
lm_knowledge_safe <- lm(rescale(knowledge_safe) ~ exp_group, data)
lm_policy_opinion <- lm(rescale(policy_opinion) ~ exp_group, data)
lm_moral_conviction <- lm(rescale(moral_conviction) ~ exp_group, data)
